%\bibitem{a}
%Author, \emph{Title}, \emph{J. Abbrev.} {\bf vol} (year) pg.
%
%\bibitem{b}
%Author, \emph{Title},
%arxiv:1234.5678.
%
%\bibitem{c}
%Author, \emph{Title},
%Publisher (year).

\bibitem{Aad:1363019}
ATLAS Collaboration, \emph{Search for new phenomena with the monojet and missing transverse momentum signature using the ATLAS detector in $\sqrt{s}$ = 7 TeV proton-proton collisions}, \emph{Phys. Lett. B} (2011), arXiv:1106.5327.

\bibitem{ATLAS-CONF-2012-147}
ATLAS Collaboration, \emph{Search for New Phenomena in Monojet plus Missing Transverse Momentum Final States using 10 fb$^{-1}$ of pp collisions at $\sqrt{s}$=8 TeV with the ATLAS detector at the LHC}, 2012, ATLAS-CONF-2012-147.

\bibitem{CMS-PAS-EXO-12-048}
CMS Collaboration, \emph{Search for new physics in monojet events in pp collisions at $\sqrt{s}$ = 8 TeV}, 2013, CMS-PAS-EXO-12-048.

\bibitem{Buckley:2013jwa}
M. r. buckley, \emph{Using effective operators to understand CoGeNT and CDMS-Si signals}, \emph{Phys.Rev."} (2013), arXiv:1308.4146.

\bibitem{Abdallah:1472683}
J. Abdallah et al., \emph{Search for new phenomena with mono-jet plus missing transverse energy signature in pp collisions at $\sqrt{s}$=8 TeV with the ATLAS detector}, 2012, ATL-COM-PHYS-2012-1211.

\bibitem{MonoZ}
N. Bell et al., \emph{Searching for Dark Matter at the LHC with a Mono-Z}, \emph{Phys.Rev.} (2012), arXiv:1209.0231.

\bibitem{MonoX}
N. Zhou, D. Berge, and D. Whiteson, \emph{Mono-everything: combined limits on dark matter production at colliders from multiple final states}, \emph{Phys.Rev.} (2013), arXiv:1302.3619.

\bibitem{ComppMSSM}
M. Cahill-Rowley et al., \emph{Complementarity and Searches for Dark Matter in the pMSSM}, 2013, arXiv:1305.6921.

\bibitem{Aad:2012ms}
ATLAS Collaboration, \emph{Further search for supersymmetry at $\sqrt{s}=7$ TeV in final states with jets, missing transverse momentum and isolated leptons with the ATLAS detector}, \emph{Phys.Rev.} (2012), arXiv:1208.4688.

\bibitem{Aad:2012fqa}
ATLAS Collaboration, \emph{Search for squarks and gluinos with the ATLAS detector in final states with jets and missing transverse momentum using 4.7 fb$^{-1}$ of $\sqrt{s}=7$ TeV proton-proton collision data}, \emph{Phys.Rev.} (2013), arXiv:1208.0949.

\bibitem{SUSY_official_paper}
ATLAS Collaboration, \emph{Search for pair-produced third-generation squarks decaying via charm quarks or in compressed supersymmetric scenarios in $pp$ collisions at $\sqrt{s}=8~$TeV with the ATLAS detector}, \emph{Phys.Rev.} (2014), arXiv:1407.0608.

\bibitem{Aad:2014wea}
ATLAS Collaboration, \emph{Search for squarks and gluinos with the ATLAS detector in final states with jets and missing transverse momentum using $\sqrt{s}=8$ TeV proton-proton collision data}, \emph{JHEP} (2014), arXiv:1405.7875.

\bibitem{EFTDM}
H. Dreiner et al., \emph{Contact Interactions Probe Effective Dark Matter Models at the LHC}, \emph{Europhys.Lett.} (2013), arXiv:1303.3348.

\bibitem{DMCons3}
J. Goodman et al., \emph{Gamma Ray Line Constraints on Effective Theories of Dark Matter}, \emph{Nucl.Phys.} (2011), arXiv:1009.0008.

\bibitem{ValidEFT}
G. Busoni et al., \emph{On the Validity of the Effective Field Theory for Dark Matter Searches at the LHC}, \emph{Phys.Lett.} (2014), arXiv:1307.2253. 

\bibitem{Buchmueller:2014yoa}
Oliver Buchmueller, Matthew J. Dolan, Sarah A. Malik and Christopher McCabe, \emph{Characterising dark matter searches at colliders and direct detection experiments: Vector mediators}, 2014, arXiv:1407.8257.

\bibitem{Kumar}
J. Kumar and D. Marfatia. \emph{Matrix element analyses of dark matter scattering and annihilation}, \emph{Phys.Rev.} (2013), arXiv:1305.1611.

\bibitem{SUSYDM}
G. Jungman et al., \emph{Supersymmetric dark matter}, \emph{Phys.Rept.} (1996).

\bibitem{METSig}
P. J. Fox et al., \emph{Missing Energy Signatures of Dark Matter at the LHC}, \emph{Phys.Rev.} (2012), arXiv:1109.4398.

\bibitem{Fox:2012ee}
P. J. Fox, R. Harnik, R. Primulando, and C-T. Yu, \emph{Taking a Razor to Dark Matter Parameter Space at the LHC}, \emph{Phys.Rev.} (2012), arXiv:1203.1662.

\bibitem{t-channel}
M. Papucci, A. Vichi, and K. M. Zurek, \emph{Monojet versus rest of the world I: t-channel Models}, \emph{JHEP} (2014), arXiv:1402.2285.

\bibitem{Bai:2010hh}
Y. Bai, P. J. Fox, and R. Harnik, \emph{The Tevatron at the Frontier of Dark Matter Direct Detection}, \emph{JHEP} (2010), arXiv:1005.3797.

\bibitem{DMCons2}
J. Goodman et al., \emph{Constraints on Dark Matter from Colliders}, \emph{Phys.Rev.} (2010), arXiv:1008.1783.

\bibitem{Fox:2011fx}
P. J. Fox, R. Harnik, J. Kopp, and Y. Tsai, \emph{LEP Shines Light on Dark Matter}, \emph{Phys.Rev.} (2011), arXiv:1103.0240.

\bibitem{Graesser:2011vj}
M. L. Graesser, I. M. Shoemaker, and L. Vecchi, \emph{A Dark Force for Baryons}, 2011, arXiv:1107.2666.

\bibitem{An:2011ck}
H. An and F. Gao, \emph{Fitting CoGeNT Modulation with an Inelastic, Isopin-Violating $Z'$ Model}, 2011, arXiv:1108.3943.

\bibitem{Chatrchyan:2013qha}
CMS Collaboration, \emph{
Search for narrow resonances using the dijet mass spectrum in pp collisions at $\sqrt{s}$ = 8TeV}, \emph{Phys.Rev.} (2013), arXiv:1302.4794.

\bibitem{Aad:2012hf}
ATLAS Collaboration, \emph{Search for high-mass resonances decaying to dilepton final states in pp collisions at s**(1/2) = 7-TeV with the ATLAS detector}, \emph{JHEP} (2012), arXiv:1209.2535.

\bibitem{Harris:2014hga}
P. Harris, V. V. Khoze, M. Spannowsky and C. Williams, \emph{Constraining Dark Sectors at Colliders: Beyond the Effective Theory Approach}, \emph{Phys.Rev.} (2015), arXiv:1411.0535.

\bibitem{CMS-PAS-EXO-12-048}
CMS Collaboration. \emph{Search for new physics in monojet events in pp collisions at $\sqrt{s}$ = 8 TeV}, 2013, CMS-PAS-EXO-12-048.

\bibitem{ATLAS-CONF-2012-147}
ATLAS Collaboration. \emph{Search for New Phenomena in Monojet plus Missing Transverse Momentum Final States using 10 fb$^{1}$ of pp collisions at $\sqrt{s}$ = 8 TeV with the ATLAS detector at the LHC}, 2012, ATLAS-CONF-2012-147.

\bibitem{Kumar:2013iva}
J. Kumar and D. Marfatia, \emph{Matrix element analyses of dark matter scattering and annihilation}, \emph{Phys.Rev.} (2013), arXiv:1305.1611.

\bibitem{Alves:2011wf}
D. Alves et al., \emph{Simplified Models for LHC New Physics Searches}, \emph{J.Phys.} (2012), arXiv:1105.2838.

\bibitem{Ade:2013zuv} 
  P.~A.~R.~Ade {\it et al.}  [Planck Collaboration],
  %``Planck 2013 results. XVI. Cosmological parameters,''
  Astron.\ Astrophys.\  {\bf 571}, A16 (2014)
  [arXiv:1303.5076 [astro-ph.CO]].

%\cite{Busoni:2014gta}
\bibitem{Busoni:2014gta} 
  G.~Busoni, A.~De Simone, T.~Jacques, E.~Morgante and A.~Riotto,
  JCAP {\bf 1503}, no. 03, 022 (2015)
  [arXiv:1410.7409 [hep-ph]].
  
\bibitem{CMS:rwa}
CMS Collaboration. \emph{Search for new physics in monojet events in pp collisions at $\sqrt{s} =$ 8 TeV}, 2013, CMS-PAS-EXO-12-048.

\bibitem{ATLAS:2012zim}
ATLAS Collaboration. \emph{Search for New Phenomena in Monojet plus Missing Transverse Momentum Final States using 10 fb$^{1}$ of pp collisions at $\sqrt{s} =$ 8 TeV with the ATLAS detector at the LHC}, 2012, ATLAS-CONF-2012-147.

\bibitem{Aad:2012ms}
ATLAS Collaboration. \emph{Further search for supersymmetry at $\sqrt{s} =$ 7 TeV in final states with jets, missing transverse momentum and isolated leptons with the ATLAS detector}, \emph{Phys.Rev.} (2012), arXiv:1208.4688.

\bibitem{Aad:2015zva}
ATLAS Collaboration. \emph{Search for new phenomena in final states with an energetic jet and large missing transverse momentum in pp collisions at $\sqrt{s}=8$ TeV with the ATLAS detector}, 2015, arXiv:1502.01518

\bibitem{CERN-THESIS-2015-038}
S. Schramm, \emph{Searching for Dark Matter with the ATLAS Detector in Events with an Energetic Jet and Large Missing Transverse Momentum}, 2015, CERN-THESIS-2015-038.

\bibitem{CooperSarkar:2011vp}
A. Cooper-Sarkar. \emph{PDFs for the LHC}, 2011, arXiv:1107.5170.

\bibitem{ATLAS:2012ky}
ATLAS Collaboration. \emph{Search for dark matter candidates and large extra dimensions in events with a jet and missing transverse momentum with the ATLAS detector}, 2013, CERN-PH-EP-2012-210, arXiV:1210.4491.

\bibitem{PJFox}
P. J. Fox et al. \emph{Missing Energy Signatures of Dark Matter at the LHC}, \emph{Phys. Rev.}, 2012.

\bibitem{NBellDent}
N. Bell, J. Dent, T. Jacques, and T. Weiler. \emph{W/Z Bremsstrahlung as the Dominant Annihilation Channel for Dark Matter}, \emph{Phys. Rev.}, 2011.

\bibitem{Aad:2014monoZlep}
ATLAS Collaboration. \emph{Search for dark matter in events with a $Z$ boson and missing transverse momentum in $pp$ collisions at $\sqrt{s}$ = 8 TeV with the ATLAS detector}, \emph{Phys.Rev.D \textbf{90}} (2014) 012004, arXiv:1404.0051.

\bibitem{MG_aMCNLO2014}
J. Alwall /emph{et al.}. \emph{The automated computation of tree-level and next-to-leading order differential cross sections, and their matching to parton shower simulations}, \emph{JHEP07} (2014) 079, arXiv:1405.0301.

\bibitem{MSTW}
A. D. Martin, W. J. Stirling, R. S. Thorne, G. Watt, \emph{Parton distributions for the LHC}, \emph{Eur.Phys.J.C63}, (2009), 189-285, arXiv:0901.0002.

\bibitem{AUtune}
ATLAS Collaboration. \emph{Summary of ATLAS Pythia8 tunes}, 2012, ATL-PHYS-PUB-2012-003.

\bibitem{Belanger:2014vza} 
  G.~Bélanger, F.~Boudjema, A.~Pukhov and A.~Semenov,
  %``micrOMEGAs4.1: two dark matter candidates,''
  Comput.\ Phys.\ Commun.\  {\bf 192}, 322 (2015)
  doi:10.1016/j.cpc.2015.03.003
  [arXiv:1407.6129 [hep-ph]].
  %%CITATION = doi:10.1016/j.cpc.2015.03.003;%%
  %53 citations counted in INSPIRE as of 15 févr. 2016
%Note sure if a better reference exists?
